Systematic studies of correlations between different order flow harmonics in $\PbPb$ collisions at $\snn = 2.76$~TeV

### 2016-12-16 longSC.tex
one more fix

To study the $p_{\rm T}$ dependence of SC$(m,n)$, we systematically vary the low $p_{\rm T}$ cut-off ($p_{\rm T, min}$), instead of using independent $p_{\rm T}$ intervals, in order to avoid large statistical fluctuations in the results. Various minimum $p_{\rm T}$ cuts from 0.2 to 1.5~GeV/$c$ are applied.
The $p_{\rm T}$ dependent results for SC(3,2) and SC(4,2) with minimum $p_{\rm T}$ cuts $0.2<p_{\rm T, min}<0.7$~GeV/$c$ are shown in Fig.~\ref{fig:Figure_2}a.
The strength of SC$(m,n)$ becomes larger as $p_{\rm T, min}$ increases. 
%This indicates that the relationship between event-by-event fluctuations of two different flow harmonics $v_m$ and $v_n$ is stronger for high $p_{\rm T}$ particles. 
These $p_{\rm T, min}$ dependent correlations have much stronger centrality dependence, with SC$(m,n)$ getting much larger as the centrality or $p_{\rm T, min}$ increase. 
NSC(3,2) and NSC(4,2) with different minimum cuts are shown in Figs.~\ref{fig:Figure_2}b and \ref{fig:Figure_2}d.
The strong $p_{\rm T, min}$ dependence observed in SC$(m,n)$ is not seen in NSC$(m,n)$. The NSC$(m,n)$ results are consistent within the errors for all $p_{\rm T, min}$ cuts. 
This indicates that the $p_{\rm T}$ dependence of SC$(m,n)$ is dominated by the $p_{\rm T}$  dependence of the $\left<v_n\right>$ values. 
The minimum $p_{\rm T}$ cuts are extended from 0.8  to 1.5~GeV/$c$ and the results are shown in Figs.~\ref{fig:Figure_2}c and \ref{fig:Figure_2}d.
While SC$(m,n)$ shows similar trends as for $p_{\rm T, min}<0.8$~GeV/$c$, NSC$(4,2)$ tends to decrease with increasing $p_{\rm T, min}$.
The $p_{\rm T, min}$ dependence of NSC(3,2) is not clearly seen and it is consistent with no $p_{\rm T, min}$ dependence within the statistical and systematic errors for the centrality range $<$~30\%, while showing a moderate decreasing trend with increasing $p_{\rm T, min}$ for the $>$~30\% centrality range.
NSC(4,2) shows a moderate decreasing trend as $p_{\rm T, min}$ increases. These observations are strikingly different from $p_{\rm T}$ dependence of the individual flow harmonics, where the relative flow fluctuations $\sigma_{v_2}/\langle v_{2} \rangle$~\cite{Voloshin:2008dg} are independent of transverse momentum up to $p_{\rm T}$ $\sim$ 8~GeV/$c$ (see Fig. 3 in Ref.~\cite{Abelev:2012di}).
%(see further discussions in Sec.~\ref{sec:ptdepsc})
%This might be an indication of possible viscous corrections for the equilibrium distribution at hadronic freeze-out~\cite{Luzum:2010ad}.
%However within the current statistical and systematic errors, it is consistent with no $p_{\rm T}$ dependence of NSC$(m,n)$ (see further discussions in Sec.~\ref{sec:ptdepsc}).

@@

It can be seen in Fig.~\ref{fig:Figure_2} that for NSC(3,2) there is no $p_{\rm T}$ dependence in the centrality range $<$30\%, and a moderate decreasing trend with increasing $p_{\rm T}$ is observed in the $>$30\% centrality range.
NSC(4,2) shows a moderate decreasing trend as $p_{\rm T}$ or centrality increases. 
In order to see the trend more clearly, we show NSC($m$,$n$) results as a function of minimum $p_{\rm T}$ cut in Figs.~\ref{fig:Figure_8} and \ref{fig:Figure_9}.

>>>>

To study the $p_{\rm T}$ dependence of SC$(m,n)$, we systematically vary the low $p_{\rm T}$ cut-off ($p_{\rm T, min}$), instead of using independent $p_{\rm T}$ intervals, in order to avoid large statistical fluctuations in the results. Various minimum $p_{\rm T}$ cuts from 0.2 to 1.5~GeV/$c$ are applied.
The $p_{\rm T}$ dependent results for SC(3,2) and SC(4,2) with minimum $p_{\rm T}$ cuts $0.2<p_{\rm T, min}<0.7$~GeV/$c$ are shown in Fig.~\ref{fig:Figure_2}a.
The strength of SC$(m,n)$ becomes larger as $p_{\rm T, min}$ increases. 
%This indicates that the relationship between event-by-event fluctuations of two different flow harmonics $v_m$ and $v_n$ is stronger for high $p_{\rm T}$ particles. 
These $p_{\rm T, min}$ dependent correlations have much stronger centrality dependence, with SC$(m,n)$ getting much larger as centrality or $p_{\rm T, min}$ increases. 
NSC(3,2) and NSC(4,2) with different minimum cuts are shown in Figs.~\ref{fig:Figure_2}b and \ref{fig:Figure_2}d.
The strong $p_{\rm T, min}$ dependence observed in SC$(m,n)$ is not seen in NSC$(m,n)$. The NSC$(m,n)$ results are consistent within the errors for all $p_{\rm T, min}$ cuts. 
This indicates that the $p_{\rm T}$ dependence of SC$(m,n)$ is dominated by the $p_{\rm T}$  dependence of the $\left<v_n\right>$ values. 
The minimum $p_{\rm T}$ cuts are extended from 0.8  to 1.5~GeV/$c$ and the results are shown in Figs.~\ref{fig:Figure_2}c and \ref{fig:Figure_2}d.
While SC$(m,n)$ shows similar trends as for $p_{\rm T, min}<0.8$~GeV/$c$, NSC$(4,2)$ tends to decrease with increasing $p_{\rm T, min}$.
The $p_{\rm T, min}$ dependence of NSC(3,2) is not clearly seen and it is consistent with no $p_{\rm T, min}$ dependence within the statistical and systematic errors for the centrality range $<$~30\%, while showing a moderate decreasing trend with increasing $p_{\rm T, min}$ for the $>$~30\% centrality range.
NSC(4,2) shows a moderate decreasing trend as $p_{\rm T, min}$ increases. These observations are strikingly different from $p_{\rm T}$ dependence of the individual flow harmonics, where the relative flow fluctuations $\sigma_{v_2}/\langle v_{2} \rangle$~\cite{Voloshin:2008dg} are independent of transverse momentum up to $p_{\rm T}$ $\sim$ 8~GeV/$c$ (see Fig. 3 in Ref.~\cite{Abelev:2012di}).
%(see further discussions in Sec.~\ref{sec:ptdepsc})
%This might be an indication of possible viscous corrections for the equilibrium distribution at hadronic freeze-out~\cite{Luzum:2010ad}.
%However within the current statistical and systematic errors, it is consistent with no $p_{\rm T}$ dependence of NSC$(m,n)$ (see further discussions in Sec.~\ref{sec:ptdepsc}).

@@

It can be seen in Fig.~\ref{fig:Figure_2} that for NSC(3,2) there is no $p_{\rm T, min}$ dependence in the centrality range $<$30\%, and a moderate decreasing trend with increasing $p_{\rm T, min}$ is observed in the $>$30\% centrality range.
NSC(4,2) shows a moderate decreasing trend as $p_{\rm T, min}$ or centrality increases. 
In order to see the trend more clearly, we show NSC($m$,$n$) results as a function of minimum $p_{\rm T}$ cut in Figs.~\ref{fig:Figure_8} and \ref{fig:Figure_9}.
